Tango-cc analysis

### 2023-12-08 stats/analysis.Rmd
add data and internal consistency

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse) # data handling etc.
library(tidybayes) # for stat_halfeye, add_predictive_draws
library(tidyboot) # for bootstrapped CIs
library(brms) # modeling
library(cmdstanr) # modeling
library(janitor) # clean_names
library(ggpubr) # ggarrange
library(ggpubr)
library(prettyR) # for describe()

# load source code for geom_flat_violin()
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")

check_cmdstan_toolchain(fix = TRUE, quiet = TRUE)

@@

```{r load_data}
dataFam <- read_csv("../data/gafo-cc-clean-data-incl-fam.csv") %>%
  filter(community != "chimfunshi") %>% 
  mutate(
         trialtype = factor(trialtype, levels = c("touch", "fam", "test")),
         agegroup = floor(ageinyears), 
         click = abs(clickdistfromtargetcenterx)/160, 
         community = factor(community, levels = c("leipzig", "hai||om", "khwe", "windhoek", "akure", "stanford"))
                      %>% recode(.,
                            leipzig = "Leipzig (Germany)",
                            akure = "Akure (Nigeria)",
                            `hai||om` = "Hai||om (Namibia)",
                            khwe = "Khwe (Namibia)",
                            windhoek = "Windhoek (Namibia)",
                            stanford = "Stanford (USA)"
                            )
         ) %>% 
  filter(!is.na(trialtype)) %>% 
  mutate_if(is.character,as.factor)

data <- read_csv("../data/gafo-cc-clean-data.csv") %>%
  filter(community != "chimfunshi" & !voiceover) %>% 
  mutate(
         agegroup = floor(ageinyears), 
         click = abs(clickdistfromtargetcenterx)/160, 
         community = factor(community, levels = c("leipzig", "hai||om", "khwe", "windhoek", "akure", "stanford"))
                      %>% recode(.,
                            leipzig = "Leipzig (Germany)",
                            akure = "Akure (Nigeria)",
                            `hai||om` = "Hai||om (Namibia)",
                            khwe = "Khwe (Namibia)",
                            windhoek = "Windhoek (Namibia)",
                            stanford = "Stanford (USA)"
                            )
         ) %>% 
  mutate_if(is.character,as.factor)

mdata <- data %>%
  mutate(
          # same as: ageinyears-mean(ageinyears)
          ageinyears = scale(ageinyears, center = T, scale = F), 
          targetcentralityx = scale(targetcentralityx),
          trialnr = scale(trialnr),
  ) %>%
  group_by(subjid, community, agegroup, ageinyears, touchscreen, household) %>%
  summarise(mean_click = mean(click)) %>%
  group_by(community) %>%
  mutate(
         household = scale(household), 
         touchscreen = factor(touchscreen),
  ) %>%
  na.omit()
```

```{r sample}
# full sample
data %>%
  group_by(community, agegroup) %>%
  summarise(n= n_distinct(subjid))

@@

# model data
mdata %>%
  group_by(community, agegroup) %>%
  summarise(n= n_distinct(subjid))

@@

```{r samplesize_plot}
ggplot(data = data %>% group_by(subjid) %>% slice(1), 
       mapping = aes(x = community, 
                     y = ageinyears, 
                     fill = community)) + 
  geom_flat_violin(scale = "count", trim = T) + 
  stat_summary(fun.data = mean_sdl,
               fun.args = list(mult = 1),
               geom = "pointrange",
               position = position_nudge(0.5)) +
  geom_dotplot(binaxis = "y",
               dotsize = 1,
               stackdir = "down",
               binwidth = 0.1,
               position = position_nudge(-0.025)) +
  theme_classic() +
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank()) + 
  guides(fill = "none") +
  scale_y_continuous(limits = c(2, 9), breaks = seq(2, 9, 1)) + 
  labs(x = "", y = "Age in years") +
  facet_grid(~ community, scales="free")
```

```{r variation}
cc_variation <- data %>% 
  summarise(
    imprecision_mean = mean(click_dist_balloons, na.rm = T) %>% round(2),
    imprecision_sd = sd(click_dist_balloons, na.rm = T) %>% round(2),
    imprecision_min = min(click_dist_balloons, na.rm = T),
    imprecision_max = max(click_dist_balloons, na.rm = T),
  )

cc_variation_communities <- data %>% 
  group_by(age_group, community) %>%
  summarise(
    imprecision_mean = mean(click_dist_balloons, na.rm = T) %>% round(2),
    imprecision_sd = sd(click_dist_balloons, na.rm = T) %>% round(2),
    imprecision_min = min(click_dist_balloons, na.rm = T),
    imprecision_max = max(click_dist_balloons, na.rm = T),
  )

cc_variation
write.csv(cc_variation, "../saves/cc_variation.csv", quote = F, row.names = F)
saveRDS(cc_variation, "../saves/cc_variation.rds")

cc_variation_communities
write.csv(cc_variation_communities, "../saves/cc_variation_communities.csv", quote = F, row.names = F)
saveRDS(cc_variation_communities, "../saves/cc_variation_communities.rds")
```

```{r variation_plot}
ggplot() +
  geom_point(data = mdata %>% filter(community == "Leipzig (Germany)"), aes(x = (ageinyears + mean(data$ageinyears)), y = mean_click, col = community), pch = 19, alpha = 0.5) +
  theme_classic() +
  scale_color_ptol(name = "Community") +
  scale_fill_ptol(name = "Community") +
  scale_x_continuous(limits = c(2, 9), breaks = seq(2, 9, 0.5)) + 
  scale_y_continuous(limits = c(0, 6), breaks = seq(0, 6, 1)) + 
  labs(x = "Age in years", y = "Average imprecision in target width")

ggplot() +
  geom_point(data = mdata, aes(x = (ageinyears + mean(data$ageinyears)), y = mean_click, col = community), pch = 19, alpha = 0.5) +
  theme_classic() +
  scale_color_ptol(name = "Community") +
  scale_fill_ptol(name = "Community") +
  scale_x_continuous(limits = c(2, 9), breaks = seq(2, 9, 0.5)) + 
  scale_y_continuous(limits = c(0, 6), breaks = seq(0, 6, 1)) + 
  labs(x = "Age in years", y = "Average imprecision in target width")
```

```{r gazefunnel}
data %>%
  group_by(targetcentralityx) %>%
  mutate(chance_upper = (targetcentralityx + 960)/2,
         chance_lower = -((targetcentralityx + 960)/2),
         center_lower = -targetcentralityx,
         center_upper = targetcentralityx) %>%
  ggplot(aes(x = targetcentralityx, y = clickdistfromtargetcenterx, col = community)) +
  labs(x = "Target centrality", y = "Imprecision") +
  geom_hline(yintercept = 0, lty = 2, size = 1, alpha = 0.75) +
  geom_point(pch = 1, alpha = 0.5) +
  scale_color_colorblind() +
  scale_x_continuous(breaks = seq(0, 960, 120)) +
  scale_y_continuous(breaks = seq(-1920, 1920, 480)) +
  theme_classic()
```

```{r clicks_bin}
clicks_bin <- data %>%
  mutate(targetposition = factor(targetposition, levels = c(1:10))) %>%
  group_by(community, targetposition) %>%
  tidyboot_mean(col = click)

ggplot(clicks_bin, aes(x = targetposition, y = mean, col = community)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), pch = 1, alpha = 1, position = position_dodge(width = .5)) +
  labs(x = "Target position (binned)", y = "Average imprecision in target width") +
  theme_classic() +
  scale_color_ptol(name = "Community") +
  scale_fill_ptol(name = "Community")
```

```{r famtrials_descriptives}
# see which trials were the most "difficult"
dataFam %>% 
  group_by(trialtype, community) %>%
  summarise(mean = mean(abs(clickdistfromtargetcenterx)), sd = sd(abs(clickdistfromtargetcenterx))) %>% 
  arrange(mean)

# identify kids that did clicked more than two balloon widths away from actual target position
dataFam %>% 
  filter(trialtype != "test" & click > 2) %>% 
  select(subjid, trialtype, agegroup, community, click) %>% 
  arrange(abs(click))

dataFam %>% 
  filter(click > 2) %>% 
  select(trialtype, agegroup, community) %>% 
  ftable()
```

```{r famtrials}
# RESOURCES:
# https://orchid00.github.io/tidy_raincloudplot
# https://www.r-bloggers.com/2021/07/ggdist-make-a-raincloud-plot-to-visualize-distribution-in-ggplot2/
# https://twitter.com/rogierk/status/1194591652452675584
# https://gist.github.com/benmarwick/b7dc863d53e0eabc272f4aad909773d2

ggplot(data = dataFam, 
       mapping = aes(x = "", 
                     y = click, 
                     fill = trialtype)) + 
  geom_flat_violin(scale = "count", 
                   trim = FALSE) + 
  stat_summary(fun.data = mean_sdl, 
               fun.args = list(mult = 1), 
               geom = "pointrange", 
               position = position_nudge(0.05)) + 
  geom_dotplot(binaxis = "y", 
               dotsize = 1, 
               stackdir = "down", 
               binwidth = 0.1, 
               position = position_nudge(-0.025)) + 
  theme(legend.position = "none") + guides(fill="none") +
  labs(x = "", 
       y = "Imprecision in balloon widths") +
  facet_grid(trialtype ~ community) + # , scales="free"
  theme_classic()
```

```{r dropouts}
dropouts <- data %>%
  group_by(subjid) %>%
  mutate(
    completedTrials = n(),
    completedStudy = ifelse(completedTrials <= 15, FALSE, TRUE), # depending on voice over included or not..
  ) %>% 
  filter(!completedStudy) %>% 
  group_by(community, agegroup) %>%
  summarise(n = n_distinct(subjid))

ggplot(dropouts, aes(x = community, y = n, fill = agegroup)) +
  geom_bar(stat="identity") + 
  theme_minimal()
```

```{r responsetime}
data %>%
  select(responsetime) %>%
  mutate(responsetime = responsetime / 1000) %>% 
  describe()

data %>% 
  ggplot(., aes((responsetime/1000))) + 
  geom_density(alpha = 0.2, fill = "grey10") + 
  geom_vline(aes(xintercept = median(clientscreenscaling)), color = "#29AF7FFF", size = 1, linetype = "longdash") +
  geom_vline(aes(xintercept = mean(clientscreenscaling, na.rm = TRUE)), color = "#FDE725FF", size = 1, linetype = "longdash")

data %>% 
  ggplot(., aes(x = (responsetime/1000), y = click)) + 
  geom_point() +
  geom_smooth(method = "lm", color = "#7D2636", alpha = 0.8) +
  stat_cor(r.accuracy = 0.01, p.accuracy = 0.01) + 
  scale_x_continuous(limits = c(0, 175), breaks = seq(0, 175, by = 50)) + 
  theme_minimal()

ggplot(data = dataFam, 
       mapping = aes(x = "", 
                     y = responsetime/1000, 
                     fill = trialtype)) + 
  geom_flat_violin(scale = "count", 
                   trim = FALSE) + 
  stat_summary(fun.data = mean_sdl, 
               fun.args = list(mult = 1), 
               geom = "pointrange", 
               position = position_nudge(0.05)) + 
  geom_dotplot(binaxis = "y", 
               dotsize = 1, 
               stackdir = "down", 
               binwidth = 0.1, 
               position = position_nudge(-0.025)) + 
  theme(legend.position = "none") + guides(fill="none") +
  labs(x = "", 
       y = "Response time") +
  facet_grid(trialtype ~ community, scales="free") +
  theme_classic()
```

>>>>

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse) # data handling etc.
library(tidybayes) # for stat_halfeye, add_predictive_draws
library(tidyboot) # for bootstrapped CIs
library(brms) # modeling
library(cmdstanr) # modeling
library(janitor) # clean_names
library(ggpubr) # ggarrange
library(splithalfr) # split half reliability
library(ggridges) # for ridge plot

@@

```{r load_data}
data <- read_csv("../data/data.csv")

mdata <- read_csv("../data/data.csv")%>%
  group_by(subjid, community, age_group, ageinyears)%>%
  summarise(impr = mean(abs(clickdistfromtargetcenterx)))%>%
  ungroup()%>%
  mutate(age = scale(ageinyears))
```

```{r sample}
# full sample
data %>%
  group_by(subjid) %>%
  summarise(n= n())%>%
  arrange(n)

data %>%
  group_by(community, age_group) %>%
  summarise(n= n_distinct(subjid))

@@

# model data
mdata %>%
  group_by(community, age_group) %>%
  summarise(n= n_distinct(subjid))

@@

# Internal consistency

```{r}
# children who did not finish all trials are removed (only 5 children total)

exclude <- data %>%
  group_by(subjid) %>%
  summarise(n= n())%>%
  filter(n < 15)%>%
  pull(subjid)

reli_data <- data%>%
  filter(!subjid %in% exclude)%>%
  mutate(pos_cent = as.character(abs(5-targetposition)))
```

## Odd-even

```{r}
reli_data%>%
  mutate(half = ifelse(trialnr %% 2 == 0, "half_1", "half_2"))%>%
  group_by(subjid, community, half)%>%
  summarise(impr = mean(abs(clickdistfromtargetcenterx)))%>%
  pivot_wider(names_from = half, values_from = impr)%>%
  group_by(community)%>%
  summarise(reli = cor(half_1, half_2))%>%
  ggplot(aes(x = reli, y = community))+
  geom_vline(xintercept = 0, lty = 3, alpha = .75)+
  geom_point(alpha = .5)+
  #geom_pointrange(aes(xmin = lci, xmax = uci))+
  scale_x_continuous(limits = c(-0.5, 1), breaks = c(-0.5, 0, 0.5, 0.6,0.7, 0.8, 0.9, 1))+
  ggtitle("Simple odd-even split")+
  theme_minimal()
```

## Stratified by target position (categorical target centrality)

```{r}
# fn_mean <- function(ds) {
#   return(mean(abs(ds$clickdistfromtargetcenterx), na.rm = TRUE))
# }
# 
# #rel <- tibble()
# 
# communities <- unique(data$community)
# 
# for (j in c(21:50)) {
# 
# for (i in communities) {
#   
# # stratified by target position
# rel_s <- by_split(
#   data = reli_data %>% filter(community == i),
#   participants = reli_data %>% filter(community == i) %>% pull(subjid),
#   fn_score = fn_mean,
#   verbose = F,
#   stratification = paste(reli_data %>% filter(community == i) %>% pull(pos_cent)),
#   careful = FALSE
# )
# 
# samp <- tibble(
#   community = i,
#   iter = j,
#   reli = split_coefs(rel_s, cor),
#   lci = split_ci(rel_s, cor)$lims["0.025","bca"],
#   uci = split_ci(rel_s, cor)$lims["0.975","bca"]
#   )
# 
# rel <- bind_rows(rel, samp)
# 
# }
# 
# }
# 
# saveRDS(rel, "../saves/stratified_internal_consistency.rds")

rel <- readRDS("../saves/stratified_internal_consistency.rds")

```

```{r}
ggplot(rel, aes(x = reli, y = community))+
  geom_vline(xintercept = 0, lty = 3, alpha = .75)+
  geom_density_ridges(col = "white", alpha = .5,rel_min_height = 0.01,)+
  geom_point(alpha = .5)+
  #geom_pointrange(aes(xmin = lci, xmax = uci))+
  scale_x_continuous(limits = c(-0.5, 1), breaks = c(-0.5, 0, 0.5, 0.6,0.7, 0.8, 0.9, 1))+
  ggtitle("Stratified by target position - no age correction")+
  theme_minimal()
```

## Stratefied and age-corrected

```{r}
# # estimate age-corrected reliability
# # run model first for one community to use update()
# split <- split_df(
#   data = reli_data %>% filter(community == "leipzig"),
#   stratification = reli_data %>% filter(community == "leipzig") %>% pull(pos_cent),
#   careful = FALSE
# )
# 
# sdata <- bind_rows(
#   split[[1]]%>%select(subjid, ageinyears, clickdistfromtargetcenterx)%>%mutate(impr = abs(clickdistfromtargetcenterx), half = "half_1"),
#   split[[2]]%>%select(subjid, ageinyears, clickdistfromtargetcenterx)%>%mutate(impr = abs(clickdistfromtargetcenterx), half = "half_2"))%>%
#   mutate(age = scale(ageinyears))
# 
# reli_age <- brm(impr ~ age + (0 + half | subjid), 
#                 data   = sdata, 
#                 family = lognormal(), 
#                 warmup = 1000, 
#                 iter   = 3000,
#                 control = list(adapt_delta = 0.95),
#                 chains = 4,
#                 cores  = 4)
# 
# # loop over communities
# 
# communities <- unique(data$community)
# 
# #model_cor <- tibble()
# 
# for (j in c(21:50)) {
#   
# for (i in communities) {
#   
# com_split <- split_df(
#   data = reli_data %>% filter(community == i),
#   stratification = reli_data %>% filter(community == i) %>% pull(pos_cent),
#   careful = FALSE
#   )
# 
# com_sdata <- bind_rows(
#   com_split[[1]]%>%select(subjid, ageinyears, clickdistfromtargetcenterx)%>%mutate(impr = abs(clickdistfromtargetcenterx), half = "half_1"),
#   com_split[[2]]%>%select(subjid, ageinyears, clickdistfromtargetcenterx)%>%mutate(impr = abs(clickdistfromtargetcenterx), half = "half_2"))%>%
#   mutate(age = scale(ageinyears))
#  
# com_mod <-  update(reli_age,
#         newdata = com_sdata,
#         warmup = 1000, 
#         iter   = 3000,
#         control = list(adapt_delta = 0.95),
#         chains = 4,
#         cores  = 4)
#   
#   cor <- summary(com_mod)$random$subjid%>%as_tibble(rownames = "parameter")%>%filter(parameter == "cor(halfhalf_1,halfhalf_2)")%>%mutate(community = i, iter = j)
# 
#   model_cor <- bind_rows(model_cor, cor)
#   
#   
#   }
#   
# }
# 
# saveRDS(model_cor, "../saves/age_corrected_internal_consistency.rds")

model_cor <- readRDS("../saves/age_corrected_internal_consistency.rds")  
```

```{r}

ggplot(model_cor, aes(x = Estimate, y = community))+
  geom_vline(xintercept = 0, lty = 3, alpha = .75)+
  geom_density_ridges(col = "white", alpha = .5, rel_min_height = 0.01,)+
  geom_point(alpha = .5)+
  #geom_pointrange(aes(xmin = `l-95% CI`, xmax = `u-95% CI`), alpha = .5)+
  ggtitle("Stratified by target position - model-based age correction")+
  scale_x_continuous(limits = c(-1, 1), breaks = c(-0.5, 0, 0.5, 0.6,0.7, 0.8, 0.9, 1))+
  theme_minimal()

```
